Report

### 2021-05-27 Rmd/report.Rmd
Update Rmd

---
title: "Report"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
---

@@

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(bilingualr)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(gt)
library(patchwork)
library(here)

# load data
participants <- readRDS(here("Results", "participants.rds"))
gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
gaze_time <- readRDS(here("Results", "gaze_time.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))

@@

# Participants

We collected data from `r length(unique(participants$participant))` participants, of which `r length(unique(participants$participant[participants$valid_participant]))` met the inclusion criteria and were included in data analyses. `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid")) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))
```

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}

# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
	facet_grid(lp~location, scales = "free") +
	geom_point(size = 3, shape = 4) +
	geom_line(aes(group = participant)) +
	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.title.y = element_blank(),
		  axis.text.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "sample_cohort.png"))
```

## Language profiles

Only valid participants.

```{r lps, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	filter(valid_participant) %>% 
	ggplot(aes(age, doe_2, colour = lp)) +
	facet_grid(test_language~location) +
	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
	geom_point(size = 3, alpha = 0.5) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 20, xmax = 22, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 24, xmax = 26, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 28, xmax = 32, ymin = -Inf, ymax = Inf) +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(labels = percent) +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(linetype = "dotted", colour = "grey"),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		axis.text.y = element_text(size = 10)
	) +
	ggsave(here("Figures", "lps.png"))
```

## Preprocessing participant data

## Preprocessing vocabulary data

@@

## Preprocessing gaze data {.tabset .tabset-pills}

@@

## {-}

@@

## Attrition rate

attrition %>%
	left_join(select(participants, location, lp, participant, date_test)) %>% 
	drop_na(trial_type) %>% 
	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

@@

### Vocabulary in the dominant language (L1)

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	mutate(age_group = as.factor(paste0(age_group, " mo"))) %>% 
	drop_na(lp) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

## Target fixations

### Target fixations: Age group and language profile {.tabset .tabset-pills}

#### Cross-sectional

For each participant and trial, the proportion of fixations to the target object were calculated from the total of fixations to the target, the distractor, and the rest of the screen. Then proportions for the same participant were aggregated within conditions, so that for each participant three data points were obtained: one in each trial type (cognate, non-cognate, and unrelated). Some participants were longitudinal. Scores form longitudinal participant  are indicated by gray lines linking data points from the same participant.

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "none",
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

#### Longitudinal

Each trial was divided into 100 ms time bins. for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin. Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated). This figure shows the fitted line of a General Additive Model (GAM) generated using the `geom_smooth()` function from the `ggplot` R package, with default settings.

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(age_group, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = interaction(participant, trial_type)), alpha = 0.5) +
	geom_violin(position = position_dodge(width = 0.5)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
	labs(x = "Age (months)", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

### Target fixations: Time course analysis

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

### Target fixations: Vocabulary size

```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_point(alpha = 0.5) +
	geom_smooth(se = FALSE, method = "lm") +
	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		  legend.position = "top",
		  axis.text.x = element_text(size = 10)) +
	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
```

### Target fixations: High vocabulary vs. low vocabulary {.tabset .tabset-pills}

```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}

gaze_time_vocab_d <- gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		time_bin = time_bin*100,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		),
		age_group = paste0(age_group, " months")
	) %>% 
	drop_na()

#### Age group: 21 months

```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "21 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~vocab_cat) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	labs(x = "Time (ms)", y = "Pr(Target fixation)", colour = "Condition", fill = "Condition") +
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"),
		  panel.grid.minor = element_blank()) +
	ggsave(here("Figures", "gaze_time.png"), height = 5, width = 7)

#### Age group: 25 months

```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

>>>>

---
title: "Report"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(bilingualr)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(here)

# create functions
logit_to_prob <- function(x) exp(x) / (1 + exp(x))

# load data
gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant)
fit <- readRDS(here("Results", "fit.rds"))

@@

## Participants {.tabset .tabpills}

* We collected data from `r length(unique(participants$participant))` participants `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.
* After applying trial- ad participant-level exclusion criteria, the sample comprise data from `r length(unique(participants$participant[participants$valid_participant]))` (`r length(unique(participants$participant[participants$valid_participant & participants$location=="Oxford"]))` tested in Oxford, and `r length(unique(participants$participant[participants$valid_participant & participants$location=="Barcelona"]))` tested in Barcelona), and were included in our analyses.
* `r length(participants$participant[duplicated(participants$participant) & participants$valid_participant])` participants in the final sample were longitudinal (tested in at least one age group). `r length(participants$participant[duplicated(participants$participant) & participants$location=="Oxford" & participants$valid_participant])` longitudinal participants were tested in Oxford and `r length(participants$participant[duplicated(participants$participant) & participants$location=="Barcelona" & participants$valid_participant])` were tested in Barcelona.
* From the longitudinal participants, `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])` were tested at two age groups, and `r length(participants$participant[(as.data.frame(table(participants$participant))$Freq>2) & participants$valid_participant])`were tested at three age groups.

### Summary

```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))

### Longitudinal

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
	geom_point(size = 2, alpha = 0.5) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	scale_colour_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	) +
	ggsave(here("Figures", "cohort.png"))
```

### Attrition (overall)

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "participants_attrition.png"))
```

### Attrition (by group)

left_join(attrition, select(participants, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant, valid_other) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

### Attrition (by participant)

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_other = mean(!valid_other),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	relocate(invalid_other, .after = invalid_vocab) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)",
		invalid_other = "Other (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab", "invalid_other")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

### Attrition (by trials)

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(valid_status = case_when(
		!valid_vocab ~ "Invalid vocabulary",
		!valid_gaze ~ "Invalid gaze",
		!valid_other ~ "Other",
		!valid_participant ~ "Invalid participant",
		TRUE ~ "Valid"
	)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_color_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(labels = scales::percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1),
		axis.text.y = element_text(size = 8),
		axis.title.y = element_blank()
	)
```

## Materials

## Procedure

## Data analysis

### Vocabulary data

@@

## Gaze data {.tabset .tabset-pills}

Each trial was divided into 100 ms time bins. for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin. Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated).

@@

@@

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(location~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

## Target fixations {.tabset .tab-pills}

### Aggregated by trial

For each participant and trial, the proportion of fixations to the target object were calculated from the total of fixations to the target, the distractor, and the rest of the screen. Then proportions for the same participant were aggregated within conditions, so that for each participant three data points were obtained: one in each trial type (cognate, non-cognate, and unrelated). Some participants were longitudinal. Scores form longitudinal participant  are indicated by grey lines linking data points from the same participant.

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, location)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_violin(position = position_dodge(width = 0.75)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

### Growth curve analysis {.tabset .tab-pills}

We fit a multilevel regression model using the `lmer` function of the `lme4` package, used the following formula:

```
elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
	(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant) +
	(1 + ot1 + ot2 + ot3 + trial_type + age_group + lp | target)
```

The formal implementation of this model is:

$$
\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
(\beta_{1} + \beta_{1p} + \beta_{1i})\times Condition_{pi} + ... \\
(\beta_{2} + \beta_{2i}) \times Group_{pi} + ... \\
(\beta_{3} + \beta_{3i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
(\beta_{4} + \beta_{4p}) \times Vocabulary_{p} + \varepsilon_{pi}
$$

#### Fixed effects

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	  tab_style(
    style = list(
      cell_fill(color = "#F9E3D6")
      ),
    locations = cells_body(
      columns = everything(),
      rows = p_value < 0.05
    )
  )
```

#### Random effects {.tabset .tab-pills}

##### By participant

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

VarCorr(fit)$participant %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
	ggplot(aes(term1, term2, fill = value)) +
	geom_tile() +
	coord_fixed() +
	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
	scale_fill_distiller(palette = "Oranges") +
	theme_bilingual() +
	theme(
		axis.title = element_blank(),
		axis.text.x = element_text(angle = 90)
	)

@@

##### By target word

```{r random_effects_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

VarCorr(fit)$target %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
	ggplot(aes(term1, term2, fill = value)) +
	geom_tile() +
	coord_fixed() +
	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
	scale_fill_distiller(palette = "Oranges") +
	theme_bilingual() +
	theme(
		axis.title = element_blank(),
		axis.text.x = element_text(angle = 90)
	)

@@

##### {-}
